Autonomous Realization of Simple Machines

### 2014-05-26 doc/paper/paper.tex
exp first figure done

In this work, we take the next step towards full autonomy where the humanoid robot, Golem Krang,
autonomously manipulates the objects in its environment to construct a simple machine. We present
an autonomous planner that perceives the available objects, specifically 15 kg cinder blocks and 10
kg 2-by-4 block blocks (e.g. potential levers), relocates them to the desired configurations output
by the constraint planner, and actuates them to flip a 45 kg load. Figure \ref{fig:showOff} demonstrates key scenes
from this scenario such as (a) detection of a cinder block, (b) locomotion with a heavy load, (c)
manipulating a lever while subject to multiple constraints and (d) application of force to the lever
leading to a successful load motion.

@@

Golem Krang is tasked with overturning a 45 kg load using a lever-fulcrum assembly with a limit of
\textcolor{red}{TBA} Nm on the force it can apply to the environment. Given the dimensions of the 
available objects in the environment, the robot has to design a structure, locate the components,
configure them into their positions and actuate the simple machine. In the following section, we
describe a typical run, focusing on details of perception, locomotion and manipulation.

@@

An interesting observation we expand on in Section 4 is about how the location of a manipulated object
and the uneven distribution of its weight over the wheels affect the locomotion accuracy. To minimize
such an artifact, in Figure \ref{fig:typical_b}, Golem Krang first moves the grasped cinder block 
to the middle of its torso before turning around and localizing the load object at 45 kg. Having
detected the load, the final configuration of the fulcrum is deduced from the assembly design and
the robot places it appropriately.

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/d.png}
  \caption{The mechanical advantage in forces}
  \label{fig:typical_d}
\end{figure}

@@

\subsection{Designs with Different Load Weights and Lever Choices}

>>>>

In this work, we take the next step towards full autonomy where the humanoid robot, Golem Krang,
autonomously manipulates the objects in its environment to construct a simple machine. We present
an autonomous planner that perceives the available objects, specifically 15 kg cinder blocks and 10
kg 2-by-4 block blocks (e.g. potential levers), relocates them to the desired configurations output
by the constraint planner, and actuates them to flip a 50 kg load. Figure \ref{fig:showOff} demonstrates key scenes
from this scenario such as (a) detection of a cinder block, (b) locomotion with a heavy load, (c)
manipulating a lever while subject to multiple constraints and (d) application of force to the lever
leading to a successful load motion.

@@

Golem Krang is tasked with overturning a 50 kg load using a lever-fulcrum assembly with a limit of
300 Nm on the force it can apply to the environment. Given the dimensions of the 
available objects in the environment, the robot has to design a structure, locate the components,
configure them into their positions and actuate the simple machine. In the following section, we
describe a typical run, focusing on details of perception, locomotion and manipulation.

@@

An interesting observation we expand on in Section 4 is about how the location of a manipulated object
and the uneven distribution of its weight over the wheels affect the locomotion accuracy. To minimize
such an artifact, in Figure \ref{fig:typical_b}, Golem Krang first moves the grasped cinder block 
to the middle of its torso before turning around and localizing the load object at 50 kg. Having
detected the load, the final configuration of the fulcrum is deduced from the assembly design and
the robot places it appropriately.

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/d.png}
  \caption{Golem Krang places the lever in the planned pose and overturns the 50 kg load.}
  \label{fig:typical_d}
\end{figure}

@@

\subsection{Designs with Different Load Weights}

To assess the ability of the proposed design algorithm, the framework is tested with two different
load sizes, 50 kg and 100 kg, where the planner needs to choose from two different levers 1.7 and 2.5
m long in each case. Once a choice is made, Golem Krang autonomously constructs the design, as
described in Section 3, and we measure the force/torque sensor readings at the end-effector of
the actuating arm. Figure \ref{fig:comparison} demonstrates the readings for the two experiments
where the maximum applied forces are 242.27 Nm and 368.63 Nm for 50 kg and 100 kg experiments
respectively. We conclude that the mechanical advantage is 2.02:1 and 2.66:1 for each case, and 
the maximum force limit is preserved; and thus, the planned design, its assembly and actuation are
successful.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.7\linewidth]{Figures/loads.png}
  \caption{The mechanical advantage in forces}
  \label{fig:comparison}
\end{figure}

\subsection{Fulcrum Base Choice and Unmodeled Implications}
